A comparison of design-based and model-based approaches for finite population spatial data -- Supporting Information.

### 2021-12-21 inst/manuscript/supporting.Rmd
style guide updates
minor update to supporting information

---
title: A comparison of design-based and model-based approaches for finite population spatial data -- Supplementary Material.
author:
  - name: Michael Dumelle
    affiliation: USEPA
    footnote: 1
  - name: Matt Higham
    affiliation: STLAW
  - name: Lisa Madsen
    affiliation: OSU
  - name: Anthony R. Olsen
    affiliation: USEPA
  - name: Jay M. Ver Hoef
    affiliation: NOAA
address:
  - code: USEPA
    address: United States Environmental Protection Agency, 200 SW 35th St, Corvallis, Oregon, 97333
  - code: STLAW
    address: Saint Lawrence University Department of Mathematics, Computer Science, and Statistics, 23 Romoda Drive, Canton, New York, 13617
  - code: OSU
    address: Oregon State University Department of Statistics, 239 Weniger Hall, Corvallis, Oregon, 97331
  - code: NOAA
    address: Marine Mammal Laboratory, Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, Washington, 98115
footnote:
  - code: 1
    text: "Corresponding Author: Michael Dumelle (Dumelle.Michael@epa.gov)"
journal: "Methods in Ecology and Evolution"
date: "`r Sys.Date()`"
linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
preamble: >
  \usepackage{bm}
  \usepackage{bbm}
  \usepackage{color}
  \DeclareMathOperator{\var}{{var}}
  \DeclareMathOperator{\cov}{{cov}}
  \renewenvironment{abstract}{}{}
output: rticles::elsevier_article
---

# Numerical Study Tables {#sec:numstudy}

@@

Recall the four design-analysis combinations and the parameter configurations, summarized in Table \ref{tab:designanalysis} and \ref{tab:parmtab}, respectively.

```{r, echo = FALSE, results = "asis"}
tab <- matrix(c("IRS-Design", "IRS-Model", "GRTS-Design", "GRTS-Model"),
       nrow = 2, byrow = TRUE) %>%
  as.table()
row.names(tab) <- c("IRS", "GRTS")
xtab1 <- xtable(tab, col.names = c("Design", "Model"), caption = "\\label{tab:designanalysis} Types of Sampling Design and Analysis combinations considered in the simulation study. The rows give the two types of sampling designs while the columns give the two types of analyses.")
align(xtab1) <- "r|ll"
names(xtab1) <- c("Design", "Model")
print(xtab1, comment = FALSE)
## I really want "Analysis" to appear as a row header and "Sampling Design" 
## to appear as a column header, but this isn't easy to figure out.
## I couldn't figure this out with xtable either so it might need to be
## made "by hand."
```

```{r, echo = FALSE, results = "asis"}
n <- c("50", "100", "200")
site_locations <- c("Random", "Gridded", "")
psill_ratio <- c("0", "0.5", "0.9")
resp_type <- c("Normal", "Lognormal", "")
parm_tab <- rbind(n, site_locations, psill_ratio, resp_type)
parm_tab[c(2, 4), 3] <- "-"
row.names(parm_tab) <- c("Sample Size (n)", "Layout", 
                         "Proportion of Dependent Error", "Response Type")
# library(knitr) kable with htlm has trouble with page breaks -- kable with latex harder for me than xtable
# kable(parm_tab, col.names = c("", "", ""),
#       caption = "\\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2 so that the partial sill was 0, 1, or 1.8.")
parm_xtab <- xtable(parm_tab, caption = "\\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2.")
align(parm_xtab) <- "r|lll"
print(parm_xtab, include.colnames = FALSE, hline.after = c(0, nrow(parm_xtab)), comment = FALSE)
```

```{r, results = "asis", eval = FALSE}
sim_one <- read_csv(here("inst", "output", "sim_one", "summ_output.csv"))
colnames(sim_one) <- c("Approach", "Bias", "RMSE", "MedAE", "Coverage", "PClose", "MedIL")
sim_one_table <- xtable(sim_one, digits = 4, caption = "Approach, mean bias (Bias), root-mean-squared error (RMSE), median absolute error (MedAE), 95 percent interval coverage (Coverage), proportion of times the approach was closer to the true value (PClose), and median interval length (MedIL)", type = "latex", latex.environments = "center", label = "tab:sim_one")
print(sim_one_table, include.rownames = FALSE, comment = FALSE)
```

Next we present a summary table for each of the 36 simulation scenarios.
```{r}
make_sim_table <- function(table_value) {
  sim_table <- read_csv(here("inst", "output", "simulation_summary", paste0("allsims", table_value, ".csv")))
  sim_table <- sim_table %>%
    dplyr::select(Approach = approach,
                  Layout = gridded,
                  Response = resptype,
                  `DE Prop` = psill_ratio,
                  n = n,
                  Bias = mpbias,
                  `rMS(P)E` = rmspe,
                  Coverage = coverage) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-Design",
       Approach == "Design IRS" ~ "IRS-Design",
       Approach == "Model GRTS" ~ "GRTS-Model",
       Approach == "Model IRS" ~ "IRS-Model"
     ),
     Layout = case_when(
        Layout ~ "Gridded",
        !Layout ~ "Random"
      ),
     Response = case_when(
       Response == "normal" ~ "Normal",
       Response == "lognormal" ~ "Lognormal"
     ),
     across(c(`DE Prop`, n), as.character)
    )
sim_table <- sim_table[c(2, 4, 1, 3), ]
sim_table_out <- xtable(
  sim_table,
  digits = 4,
  caption = "Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\\% interval coverage (Coverage) for a simulation scenario.",
   type = "latex",
  latex.environments = "center"
)
print(sim_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.85")
}
```

>>>>

---
title: A comparison of design-based and model-based approaches for finite population spatial data -- Supporting Information.
author:
  - name: Michael Dumelle
    affiliation: USEPA
    footnote: 1
  - name: Matt Higham
    affiliation: STLAW
  - name: Lisa Madsen
    affiliation: OSU
  - name: Anthony R. Olsen
    affiliation: USEPA
  - name: Jay M. Ver Hoef
    affiliation: NOAA
address:
  - code: USEPA
    address: United States Environmental Protection Agency, 200 SW 35th St, Corvallis, Oregon, 97333
  - code: STLAW
    address: Saint Lawrence University Department of Mathematics, Computer Science, and Statistics, 23 Romoda Drive, Canton, New York, 13617
  - code: OSU
    address: Oregon State University Department of Statistics, 239 Weniger Hall, Corvallis, Oregon, 97331
  - code: NOAA
    address: Marine Mammal Laboratory, Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, Washington, 98115
footnote:
  - code: 1
    text: "Corresponding Author: Michael Dumelle (Dumelle.Michael@epa.gov)"
journal: "Methods in Ecology and Evolution"
date: "`r Sys.Date()`"
linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
preamble: >
  \usepackage{bm}
  \usepackage{bbm}
  \usepackage{color}
  \DeclareMathOperator{\var}{{var}}
  \DeclareMathOperator{\cov}{{cov}}
  \renewenvironment{abstract}{}{}
output: rticles::elsevier_article
---

# Simulation Study Tables {#sec:simtabs}

@@

Recall the four sampling-analysis combinations from the simulation study, summarized in Table \ref{tab:designanalysis}. Also recall the 36 parameter configurations from the simulation study, summarized in Table \ref{tab:parmtab}.

```{r, echo = FALSE, results = "asis"}
tab <- matrix(c("IRS-Design", "IRS-Model", "GRTS-Design", "GRTS-Model"),
       nrow = 2, byrow = TRUE) %>%
  as.table()
row.names(tab) <- c("IRS", "GRTS")
xtab1 <- xtable(tab, col.names = c("Design", "Model"), caption = "\\label{tab:designanalysis} Sampling-analysis combinations in the simulation study. The rows give the two types of sampling designs and the columns give the two types of analyses.")
align(xtab1) <- "r|ll"
names(xtab1) <- c("Design", "Model")
print(xtab1, comment = FALSE)
## I really want "Analysis" to appear as a row header and "Sampling Design" 
## to appear as a column header, but this isn't easy to figure out.
## I couldn't figure this out with xtable either so it might need to be
## made "by hand."
```

```{r, echo = FALSE, results = "asis"}
n <- c("50", "100", "200")
site_locations <- c("Random", "Gridded", "")
psill_ratio <- c("0", "0.5", "0.9")
resp_type <- c("Normal", "Lognormal", "")
parm_tab <- rbind(n, site_locations, psill_ratio, resp_type)
parm_tab[c(2, 4), 3] <- "-"
row.names(parm_tab) <- c("Sample Size (n)", "Layout", 
                         "Proportion of Dependent Error", "Response Type")
# library(knitr) kable with htlm has trouble with page breaks -- kable with latex harder for me than xtable
# kable(parm_tab, col.names = c("", "", ""),
#       caption = "\\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2 so that the partial sill was 0, 1, or 1.8.")
parm_xtab <- xtable(parm_tab, caption = "\\label{tab:parmtab} Simulation scenario options. All combinations of sample size, location layout, response type, and proportion of dependent random error composed the 36 simulation scenarios. In each simualtion scenario, the total variance was 2.")
align(parm_xtab) <- "r|lll"
print(parm_xtab, include.colnames = FALSE, hline.after = c(0, nrow(parm_xtab)), comment = FALSE)
```

Next we present tables summarizing mean estimation bias (design-based) or mean prediction bias (model-based), root-mean-squared error (design-based) or root-mean-squared-prediction error (model-based), and 95% confidence interval coverage (design-based) or 95% prediction interval coverage (model-based) for all 36 simulation scenarios.
```{r}
make_sim_table <- function(table_value) {
  sim_table <- read_csv(here("inst", "output", "simulation_summary", paste0("allsims", table_value, ".csv")))
  sim_table <- sim_table %>%
    dplyr::select(Approach = approach,
                  Layout = gridded,
                  Response = resptype,
                  `DE Prop` = psill_ratio,
                  n = n,
                  Bias = mpbias,
                  `rMS(P)E` = rmspe,
                  Coverage = coverage) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-Design",
       Approach == "Design IRS" ~ "IRS-Design",
       Approach == "Model GRTS" ~ "GRTS-Model",
       Approach == "Model IRS" ~ "IRS-Model"
     ),
     Layout = case_when(
        Layout ~ "Gridded",
        !Layout ~ "Random"
      ),
     Response = case_when(
       Response == "normal" ~ "Normal",
       Response == "lognormal" ~ "Lognormal"
     ),
     across(c(`DE Prop`, n), as.character)
    )
sim_table <- sim_table[c(2, 4, 1, 3), ]
sim_table_out <- xtable(
  sim_table,
  digits = 4,
  caption = paste0("Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\\% interval coverage (Coverage) in simulation scenario ", table_value, "."),
   type = "latex",
  latex.environments = "center",
  align = c("llllrrrrr")
)
print(sim_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.85")
}
```

### 2021-12-21 inst/manuscript/supporting.tex
minor update to supporting information

Recall the four design-analysis combinations and the parameter
configurations, summarized in Table \ref{tab:designanalysis} and
\ref{tab:parmtab}, respectively.

\begin{table}[ht]
\centering
\begin{tabular}{r|ll}
  \hline
 & Design & Model \\ 
  \hline
IRS & IRS-Design & IRS-Model \\ 
  GRTS & GRTS-Design & GRTS-Model \\ 
   \hline
\end{tabular}
\caption{\label{tab:designanalysis} Types of Sampling Design and Analysis combinations considered in the simulation study. The rows give the two types of sampling designs while the columns give the two types of analyses.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{r|lll}
   \hline
Sample Size (n) & 50 & 100 & 200 \\ 
  Layout & Random & Gridded & - \\ 
  Proportion of Dependent Error & 0 & 0.5 & 0.9 \\ 
  Response Type & Normal & Lognormal & - \\ 
   \hline
\end{tabular}
\caption{\label{tab:parmtab} Simulation parameters. Total variability for all scenarios was 2.} 
\end{table}

Next we present a summary table for each of the 36 simulation scenarios.

@@

\begin{tabular}{lllllrrr}

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

@@

\caption{Approach, layout (Layout), response type (Response) roportion of dependent error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) for a simulation scenario.} 

>>>>

Recall the four sampling-analysis combinations from the simulation
study, summarized in Table \ref{tab:designanalysis}. Also recall the 36
parameter configurations from the simulation study, summarized in Table
\ref{tab:parmtab}.

\begin{table}[ht]
\centering
\begin{tabular}{r|ll}
  \hline
 & Design & Model \\ 
  \hline
IRS & IRS-Design & IRS-Model \\ 
  GRTS & GRTS-Design & GRTS-Model \\ 
   \hline
\end{tabular}
\caption{\label{tab:designanalysis} Sampling-analysis combinations in the simulation study. The rows give the two types of sampling designs and the columns give the two types of analyses.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{r|lll}
   \hline
Sample Size (n) & 50 & 100 & 200 \\ 
  Layout & Random & Gridded & - \\ 
  Proportion of Dependent Error & 0 & 0.5 & 0.9 \\ 
  Response Type & Normal & Lognormal & - \\ 
   \hline
\end{tabular}
\caption{\label{tab:parmtab} Simulation scenario options. All combinations of sample size, location layout, response type, and proportion of dependent random error composed the 36 simulation scenarios. In each simualtion scenario, the total variance was 2.} 
\end{table}

Next we present tables summarizing mean estimation bias (design-based)
or mean prediction bias (model-based), root-mean-squared error
(design-based) or root-mean-squared-prediction error (model-based), and
95\% confidence interval coverage (design-based) or 95\% prediction
interval coverage (model-based) for all 36 simulation scenarios.

@@

\begin{tabular}{lllrrrrr}

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 19.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 20.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 21.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 22.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 23.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 24.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 25.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 26.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 27.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 28.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 29.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 30.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 31.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 32.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 33.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 34.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 35.} 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 36.} 
